### 2020-07-24 README.Rmd
Update dictionary

Note that instead of using a whole batch and then leave a single sample on the third distributes all the samples in the three batches that will be needed.
We cann directly look for the distribution of the samples given our max number of samples per batch:

@@

The CRAN task View of [Experimental Design](https://CRAN.R-project.org/view=ExperimentalDesign) includes many packages rellevant for designing an experiment before collecting data, but none of them provides how to manage them once the samples are already collected.

>>>>

Note that instead of using a whole batch and then leave a single sample on the third distributes all the samples in the three batches that will be needed.
We can directly look for the distribution of the samples given our max number of samples per batch:

@@

The CRAN task View of [Experimental Design](https://CRAN.R-project.org/view=ExperimentalDesign) includes many packages relevant for designing an experiment before collecting data, but none of them provides how to manage them once the samples are already collected.
